Computation and comparison of the stable northeastern United States marine boundary layer

### 2020-12-07 Paper/results.tex
updated vertical velocity plots

%%%%%%%%%%% z=20 m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \begin{tikzpicture}
    % 5 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,4.50in)
         {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 4.50in){(a) horizontal vel., stable 5 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,4.35in)
         {\includegraphics[width=3.20in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 4.50in){(b) vertical vel., stable 5 m/s};

    % 10 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,2.25in)
         {\includegraphics[width=3in]{figures/snapshots/10ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 2.25in){(c) horizontal vel., stable 10 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,2.10in)
         {\includegraphics[width=3.20in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 2.25in){(d) vertical vel., stable 10 m/s};

    % 15 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,0in)
         {\includegraphics[width=3in]{figures/snapshots/15ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 0in){(e) horizontal vel., stable 15 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,-0.15in)
         {\includegraphics[width=3.20in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 0in){(f) vertical vel., stable 15 m/s};

>>>>

%%%%%%%%%%% z=20 m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \begin{tikzpicture}
    % 5 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,4.50in)
         {\includegraphics[width=3in]{figures/snapshots/05ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 4.50in){(a) horizontal vel., stable 5 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,4.45in)
         {\includegraphics[width=3.50in]{figures/snapshots/05ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 4.50in){(b) vertical vel., stable 5 m/s};

    % 10 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,2.25in)
         {\includegraphics[width=3in]{figures/snapshots/10ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 2.25in){(c) horizontal vel., stable 10 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,2.20in)
         {\includegraphics[width=3.50in]{figures/snapshots/10ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 2.25in){(d) vertical vel., stable 10 m/s};

    % 15 m/s plots
    \node[anchor=south west, inner sep=0](image) at (0in,0in)
         {\includegraphics[width=3in]{figures/snapshots/15ms/velh_mag_z20.png}};
    \node[align=left] at (1in, 0in){(e) horizontal vel., stable 15 m/s};
    \node[anchor=south west, inner sep=0](image) at (3in,-0.05in)
         {\includegraphics[width=3.50in]{figures/snapshots/15ms/velz_z20_samelimits.png}};
    \node[align=left] at (4.25in, 0in){(f) vertical vel., stable 15 m/s};
